BivData Setup

### 2020-01-28 results/Chapter3_ideas99.Rmd
in the middle of work and ideas

#read files
whole.cell.data <- read.csv("~./MLH1repo/whole_cell_measures.csv")
#load(file="~./MLH1repo/data/CleanBivData.RData")#added batch17
```

@@

@@

female.biv.count_table$ratio.now <- var(refMus.geome_Mb_XX) / female.biv.count_table$var_sc
female.biv.count_table$ratio.invert <-  female.biv.count_table$var_sc / var(refMus.geome_Mb_XX)

@@

>>>>

#read files
whole.cell.data <- read.csv("~./MLH1repo/whole_cell_measures.csv")

#load(file="C:/Users/alpeterson7/Documents/MLH1repo/data/MLH1/MLH1_data_setup_1.5.20.RData")#added batch18
#load(file="~./MLH1repo/data/CleanBivData.RData")#added batch17
```

@@

whole.cell.data <- whole.cell.data[!(is.na(whole.cell.data$SC.length) | whole.cell.data$SC.length==""), ]

@@

female.biv.count_table$ratio.now <- var(refMus.geome_Mb_XX) / female.biv.count_table$var_sc

female.biv.count_table$ratio.invert <-  female.biv.count_table$var_sc / var(refMus.geome_Mb_XX)

#plot these variances, do them for male and female

@@

```{r var.ratios.plot, echo=FALSE}

#var(refMus.geome_Mb_XX) #1146.608
#var(refMus.geome_Mb_male) #1109.412

#female.biv.count_table, table of 18 cells with their summary stats

female.cell.var.ratios <- ggplot(female.biv.count_table, aes(ratio.now, fileName))+geom_point()
female.cell.var.ratios

male.cell.var.ratios <- ggplot(male.biv.count_table, aes(ratio.now, fileName))+geom_point()
male.cell.var.ratios

female.biv.count_table$sex <- "female"
male.biv.count_table$sex <- "male"

biv.ratio.table <- rbind(female.biv.count_table, male.biv.count_table)

biv.ratio.table <- add_mouse(biv.ratio.table)
biv.ratio.table <- add_strain(biv.ratio.table)

all.ratios <- ggplot(biv.ratio.table, aes(y=ratio.now, x=strain, color=strain))+geom_jitter()+facet_wrap(~sex)+ggtitle("")+ylab(" var(chrm size Mb) : var(SC lengths)")+theme_bw()

A question which is fundamental to these Chap3 analyses:

 - Is chrom axis compaction an accurate reflection on the actual physical chrm size? (is ranked SC length a decent predictor for chromosome identity?)

Trying to address this by calculating the ratio between the within cell variance of SC lengths and the variance of chromsomes, ohysical sizes (mb) (haploid sizes from ref genome)

The variance across SC is always smaller than variance across chrm sizes. could be due to different resolution of microscope (SC).

what is a better name for this ratio? Chrm size variation (mB), and bivalent length variation (uM)

true compaction ratio, compaction fedelity ratio, ... it's a ratio of variances, so those might be not be the best choices

there is a negative relatioship with total SC and this ratio

- is total SC a good metric for comparing with this?

-is it strange that males have a clear min/higher min?

-do the strains cluster with their ratios? ... still unbalanced data

Male cell ratios are mostly

above are ratios for indiviual cells, ratio of the variance of the physical chrm lengths (predicted, no centromere or telomere) to the variance of bivalents in SC.

### 2020-01-28 src/BivData_Setup.Rmd
in the middle of work and ideas

@@

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.27.20.RData")
#save.image("data/BivData_4_PCA.RData")

@@

- chrom class proportions

- SC lengths, by CO number

>>>>

check the numbers of bivalents with a SC length, but no hand.foci.count

@@

#check the numbers of bivalents with a SC length, but no hand.foci.count

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.28.20.RData")
#save.image("data/BivData_4_PCA.RData")

@@

-chrom class proportions

-SC lengths, by CO number
